WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-07-31 ms.tex
Bump DCC version
Add detector references

The \acf{LIGO} and Virgo will soon begin taking data \cite{LIGOObservingScenarios} in their `Advanced' configurations, ultimately increasing their reach in volume within the local Universe by three orders of magnitude as compared to their initial configurations through 2010. They will form the first parts of a sensitive global \ac{GW} detector network, to be later augmented by the Japanese KAGRA facility \cite{LCGT,KAGRAInterferometerDesign} and \ac{LIGO}\nobreakdashes--India \cite{LIGOIndia}.

@@

\begin{acknowledgements}
This paper has LIGO Document Number LIGO\nobreakdashes-P1500009\nobreakdashes-v1.

>>>>

The \acl{LIGO} (\acsu{LIGO}; \cite{AdvancedLIGOHarry,AdvancedLIGO}) and Virgo \cite{AdvancedVirgo} will soon begin taking data \cite{LIGOObservingScenarios} in their `Advanced' configurations, ultimately increasing their reach in volume within the local Universe by three orders of magnitude as compared to their initial configurations through 2010. They will form the first parts of a sensitive global \ac{GW} detector network, to be later augmented by the Japanese KAGRA facility \cite{LCGT,KAGRAInterferometerDesign} and \ac{LIGO}\nobreakdashes--India \cite{LIGOIndia}.

@@

\begin{acknowledgements}
This paper has LIGO Document Number LIGO\nobreakdashes-P1500009\nobreakdashes-v2.
